Untwisting the Tetrahelix (v0.5)

### 2017-02-18 doc/TetrahelixUntwist.tex
some improvements

@@

To Be Done: I need to see if the one-hop formulat can be simplified.
Compute the two-hop formula and test that it gives length 1 when the BC constants. -- YES!

By similar algebra and trigonometry:
\begin{align*}
  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
\end{align*}

Note: it is not clear I am allowed to do this, because the two-hop function is different!

Let $f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)$.
Let $g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)$.

\begin{align*}
  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{1}{9} + r_{\rho}^2f_{\rho}} 
\end{align*}

If the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
we will opitmize the overall minimax distance by choosing the largest radius
up until one-hop $= 1$, the rail-edge length. Numerical test suggests that this is true.

>>>>

\begin{figure}[H] %float with two figures
  \label{series}
  \centering
     \includegraphics[width=0.95\textwidth]{figures/BCHelixCloseUp.png}
     \caption{BC Helix Close-up}
\end{figure}

@@

By similar algebra and trigonometry:
\begin{align*}
  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
\end{align*}

We would really like to know the partial derivative of the two-hops - one-hop with respect
to the radius to be able to understand how to choose the radius to form the minimimax optimum.

Let:
\begin{equation}
  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9}
  \end{equation}
\begin{equation}
  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} 
\end{equation}

\begin{equation}
  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)
\end{equation}
\begin{equation}
  k_{\rho} = (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)
\end{equation}

Then:
\begin{align*}
  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}
  - \sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }
\end{align*}

% Using wolfram alph we se this derivate remains negative in this range....
% plot d/dr sin(2r/3 + 4pi/3)^2 - sin(r/3 + 2pi/3)^2 + (1 - cos(2r/3 + 4pi/3))^2 -(1-cos(r/3 + 2pi/3))^2 from 0 to 35.44 degrees
% in other words

% This part is also negative withing this range...
%  d/dr -(16/9)sin(r/2)^2 - -(4/9)sin(r/2)^2 from 0 to 35.44 degrees

%% Using Mathematica, I get:
%% f[x_, r_] := 
%%  Sqrt[4/9 + 
%%     x^2 (-16 Sin[r/2]^2/9 + 
%%        Sin[2 r/3 + 4 Pi /3]^2 + (1 - Cos[2 r/3 + 4 Pi/3])^2)] - 
%%   Sqrt[1/9 + 
%%     x^2*(-4*Sin[r/2]^2/9 + 
%%        Sin[r/3 + 2 Pi/3]^2 + (1 - Cos[r/3 + 2 Pi/3])^2) ]
%% N[N[f[1, 1]]]

%% Plot3D[D[f[x, r]], {x, 0, 2}, {r, 0, Pi}]

%% This grahp demonstrates the derivative is always negative.

By graph inspection using Mathematica, we see the partial derivative of this with respect to
radius $r_{\rho}$ is always negative.
Since the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
we will opitmize the overall minimax distance by choosing the largest radius
up until one-hop $= 1$, the rail-edge length. Numerical test suggests that this is true.
